Galaxy Zoo: the dependence of the star formation-stellar mass relation on spiral disk morphology

### 2015-02-11 paper/mainsequence_morph.tex
Added journal macros and fixed figure paths for arXiv submission

@@

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_arms_number_weighted_contour.pdf}
\caption{Total star formation rate as a function of stellar mass; grayscale colors are the distribution of all star-forming galaxies in SDSS from the MPA-JHU DR7 catalog. Coloured contours in each panel show spiral galaxies weighted by the GZ2 likelihoods of hosting 1, 2, 3, 4, more than four, or ``uncertain'' numbers of spiral arms, respectively. Dotted lines show the weighted least-squares linear fit to each population as split by arm multiplicity; the solid line is the fit to all star-forming galaxies. 
\label{fig-number}}
\end{figure*}

@@

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_arms_winding.pdf}
\caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}. From left to right: red, green, and blue points are spiral galaxies with ``tight'', ``medium'', and ``loose'' winding spiral arms as identified by GZ2 morphology flags. Dotted lines show the weighted least-squares linear fit as split by pitch angle; the solid line is the fit to all star-forming galaxies. The slight positive offset in SFR for loosely-wound spiral arms is interpreted as contamination by merging pairs of galaxies (Section~\ref{sec-discussion}).
\label{fig-winding}}
\end{figure*}

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_arms_winding_weighted.pdf}
\caption{Same as Figure~\ref{fig-winding}, but with colormaps showing all spiral galaxies weighted by the GZ2 vote fractions for ``tight'', ``medium'', and ``loose'' winding spiral arms. 
\label{fig-winding_weighted}}
\end{figure*}

@@

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_bar_contour.pdf}
\caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}. Left: blue contours show the distribution of barred galaxies ($p_\textrm{bar}\ge0.4$ for previously-identified disks) from GZ2. Right: red contours are the distribution of remaining disk galaxy population with no evidence for a strong bar ($p_\textrm{bar}<0.4$). Dotted lines show the weighted least-squares linear fit to the barred/unbarred population; the solid line is the fit to all star-forming galaxies. 
\label{fig-bar}}
\end{figure*}

@@

\begin{figure}
\includegraphics[angle=0,width=3.5in]{figures/masslim/sigma_mstar.pdf}
\caption{Width of the star-forming main sequence ($\sigma_{SFR}$) as a function of stellar mass, as measured by the sample standard deviation. Black points represent the entire star-forming population. Disk subsamples are overplotted as solid lines; colours are the same as the respective plots in Figures~\ref{fig-number}, \ref{fig-winding}, \ref{fig-bar} and \ref{fig-mergers}. Morphological categories or mass ranges with fewer than 10 galaxies/bin are not plotted; this includes all galaxies with 3, 4, and 5+ spiral arms.
\label{fig-sigma}}
\end{figure}

@@

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_mergers_both.pdf}
\caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}. Left: Coloured points show 2,978~merging galaxies from \citet{dar10a}. Mergers are colour-coded by the mass ratio of the primary and secondary galaxies; there is no clear difference in the merging populations with regard to the SFMS when comparing major to minor mergers. When fixing the slope of the star-forming main sequence and allowing the offset to vary, mergers (dotted line) have higher SFRs by $\sim0.3$~dex compared to all star-forming galaxies (solid line). Right: Star-forming galaxies binned and colour-coded by merger fraction ($N_\textrm{mergers}/N_\textrm{star-forming galaxies})$. Overplotted lines are the same as left plot. Of the galaxies that lie furthest above the SFMS, more than $50\%$ are unambiguous mergers. 
\label{fig-mergers}}
\end{figure*}

>>>>

\input macros.tex

@@

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{ms_arms_number_weighted_contour.pdf}
\caption{Total star formation rate as a function of stellar mass; grayscale colors are the distribution of all star-forming galaxies in SDSS from the MPA-JHU DR7 catalog. Coloured contours in each panel show spiral galaxies weighted by the GZ2 likelihoods of hosting 1, 2, 3, 4, more than four, or ``uncertain'' numbers of spiral arms, respectively. Dotted lines show the weighted least-squares linear fit to each population as split by arm multiplicity; the solid line is the fit to all star-forming galaxies. 
\label{fig-number}}
\end{figure*}

@@

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{ms_arms_winding.pdf}
\caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}. From left to right: red, green, and blue points are spiral galaxies with ``tight'', ``medium'', and ``loose'' winding spiral arms as identified by GZ2 morphology flags. Dotted lines show the weighted least-squares linear fit as split by pitch angle; the solid line is the fit to all star-forming galaxies. The slight positive offset in SFR for loosely-wound spiral arms is interpreted as contamination by merging pairs of galaxies (Section~\ref{sec-discussion}).
\label{fig-winding}}
\end{figure*}

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{ms_arms_winding_weighted.pdf}
\caption{Same as Figure~\ref{fig-winding}, but with colormaps showing all spiral galaxies weighted by the GZ2 vote fractions for ``tight'', ``medium'', and ``loose'' winding spiral arms. 
\label{fig-winding_weighted}}
\end{figure*}

@@

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{ms_bar_contour.pdf}
\caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}. Left: blue contours show the distribution of barred galaxies ($p_\textrm{bar}\ge0.4$ for previously-identified disks) from GZ2. Right: red contours are the distribution of remaining disk galaxy population with no evidence for a strong bar ($p_\textrm{bar}<0.4$). Dotted lines show the weighted least-squares linear fit to the barred/unbarred population; the solid line is the fit to all star-forming galaxies. 
\label{fig-bar}}
\end{figure*}

@@

\begin{figure}
\includegraphics[angle=0,width=3.5in]{sigma_mstar.pdf}
\caption{Width of the star-forming main sequence ($\sigma_{SFR}$) as a function of stellar mass, as measured by the sample standard deviation. Black points represent the entire star-forming population. Disk subsamples are overplotted as solid lines; colours are the same as the respective plots in Figures~\ref{fig-number}, \ref{fig-winding}, \ref{fig-bar} and \ref{fig-mergers}. Morphological categories or mass ranges with fewer than 10 galaxies/bin are not plotted; this includes all galaxies with 3, 4, and 5+ spiral arms.
\label{fig-sigma}}
\end{figure}

@@

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{ms_mergers_both.pdf}
\caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}. Left: Coloured points show 2,978~merging galaxies from \citet{dar10a}. Mergers are colour-coded by the mass ratio of the primary and secondary galaxies; there is no clear difference in the merging populations with regard to the SFMS when comparing major to minor mergers. When fixing the slope of the star-forming main sequence and allowing the offset to vary, mergers (dotted line) have higher SFRs by $\sim0.3$~dex compared to all star-forming galaxies (solid line). Right: Star-forming galaxies binned and colour-coded by merger fraction ($N_\textrm{mergers}/N_\textrm{star-forming galaxies})$. Overplotted lines are the same as left plot. Of the galaxies that lie furthest above the SFMS, more than $50\%$ are unambiguous mergers. 
\label{fig-mergers}}
\end{figure*}
